$3$-D Weak Lensing Mass Map Reconstruction: Reducing the line of sight smearing

### 2020-12-22 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex

We select peaks with values greater than an ad-hoc threshold as candidates of
galaxy clusters following \citet{HSC1-massMap-cluster}.  The threshold is set
to a few times the standard deviation of the noise peaks. We use different
detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters
from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and
middle columns of Figure \ref{fig_detFalsRateNFW} show the detection rates for
halos in the (mass, redshift) planes with detection thresholds set to
$1.5\sigma$ and $3.0\sigma$ of the noise peaks' distributions, respectively.
The right column of Figure \ref{fig_detFalsRateNFW} shows the corresponding
numbers of false detections per square degree as functions of detection
thresholds. The first, second, and third rows of Figure
\ref{fig_detFalsRateNFW} correspond to the $lambda=3.5,4.0,5.0$, respectively.

>>>>

With the intent to suppress false detections, we select peaks with values
greater than an ad-hoc threshold as candidates of galaxy clusters following
\citet{HSC1-massMap-cluster}.  The threshold is set to a few times the standard
deviation of the noise peaks. We use different detection thresholds
($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters from the mass maps
reconstructed with $\lambda=3.5,4.0,5.0$. The left and middle columns of Figure
\ref{fig_detFalsRateNFW} show the detection rates for halos in the (mass,
redshift) planes with detection thresholds set to $1.5\sigma$ and $3.0\sigma$
of the noise peaks' distributions, respectively.  The right column of Figure
\ref{fig_detFalsRateNFW} shows the corresponding numbers of false detections
per square degree as functions of detection thresholds. The first, second, and
third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
$lambda=3.5,4.0,5.0$, respectively.

### 2020-12-22 doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex

The regularization parameter ($\lambda$) for the preliminary lasso is set to
$3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
propose to incorporate external group information into different adaptive lasso
penalization weights by setting the penalization weights for projection
coefficients in the same group to the average of the adaptive weights in this
group, we smooth the preliminary lasso estimation in each lens redshift bin
with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc. The smoothed
preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
the penalization weights are set to
$\hat{w}=1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
The regularization parameter for the adaptive lasso is set to
$\lambda_{\rm{ada}}=\lambda$.
As we have done on the NFW dictionary's reconstruction, we smooth the
reconstructed density maps with the Gaussian kernel (scale radius equals
$1.\arcmin 5$) in each lens redshift plane.

@@

\begin{figure*}
\centering
\subfigure[Point Mass: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=5.0$]{
        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
        }
\caption{The density maps reconstructed from the mock galaxy shape catalog with
    the point mass dictionary. The penalization parameters are $\lambda=3.5$
    (left) and $\lambda=5.0$ (right).  The input halo mass is
    $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The
    vertical direction is the line of sight direction. The boxes' lower
    boundaries and upper boundaries of correspond to $z=0.01$ and $z=0.85$,
    respectively.
    } \label{fig_PM3D}
\end{figure*}

>>>>

The regularization parameter ($\lambda$) for the preliminary lasso is set to
$3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
propose to incorporate external group information into different adaptive lasso
penalization weights by setting the penalization weights for projection
coefficients in the same group to the average of the adaptive weights in this
group, we smooth the preliminary lasso estimation in each lens redshift bin
with a top-hat filter of comoving diameter: $0.25~h^{-1}$ Mpc. The smoothed
preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
the penalization weights are set to
$\hat{w}=1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.

@@

\begin{figure*}
\centering
\begin{minipage}[c]{1.0\columnwidth}
    \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
    \centering
    \small Point Mass: $\lambda=3.5$
\end{minipage}
\begin{minipage}[c]{1.0\columnwidth}
    \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
    \centering
    \small Point Mass: $\lambda=5.0$
\end{minipage}
\caption{The density maps reconstructed from the mock galaxy shape catalog with
    the point mass dictionary. The penalization parameters are $\lambda=3.5$
    (left) and $\lambda=5.0$ (right).  The input halo mass is
    $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$, and its redshift is $z=0.164$.  The
    vertical direction is the line of sight direction. The boxes' lower
    boundaries and upper boundaries of correspond to $z=0.01$ and $z=0.85$,
    respectively.
    } \label{fig_PM3D}
\end{figure*}
